\subsection{Results: Student assistant}
Our student assistant gave us a lot of valued response on both how we executed the test and how our system worked. The changes suggested to our execution were extremely helpful before our second testgroup, and included the following:
\begin{enumerate}
\item Select a test leader and a person to serve as your system.
\item Test leader should introduce the test, pointing out that it's the system that's being tested. 
\item Test subject should be given a set of scenarios or tasks to properly test the system. 
\item Test subject should be informed that (s)he may abort the test at any time.
\item Test subject should not be assisted in any way once the test starts.
\item Only the test leader should hold a dialog with the test subject.
\item The remaining members should be observing and noting any difficulties occuring during the test.
\end{enumerate}

The suggestions for the paper prototype included the following points:
\begin{enumerate}
\item The notifications popup was a bit difficult to understand because of a lack of division between elements in the list.
\item There was no support for clicking at a desired time and date directly in the calendar to create a new appointment.
\item When editing or creating an appointment the list of meeting rooms didn't show how many participants a room could hold.
\item When editing or creating an appointment it's not intuitive how to add more members.
\end{enumerate}

\subsection{Results: Other group}
\begin{enumerate}
\item The test subject could not find the dates for the weekdays in the calendar view.
\end{enumerate}