\documentclass[a4paper, 10pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[norsk]{babel}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tabularx}
\usepackage{color, colortbl}

\definecolor{Gray}{gray}{0.9}

\begin{document}




\begin{tabularx}{\textwidth}{ |X|X| }
\hline
\rowcolor{Gray}
Test ID & \# 10 \\ \hline
Test item & Book meeting room \\ \hline
Approach & Possibility to book a meeting room from availible rooms. Calendar will create a list of non-booked meeting rooms for the selected timeframe. User can pick a room from this list. Booked meeting rooms will be made availible if an appointment is deleted or cancelled.\\ \hline
Item pass/ fail criteria & When creating an appointment the user is be able to book a meeting room from a list of availible meeting rooms. The list will only contain non-booked meeting rooms, and will be updated accordingly when a room is booked or made availible.\\ \hline
Input data & 
\begin{itemize}
	\item Desired timeframe
	\item List of rooms
	\item Cancel appointment
	\item Delete appointment
\end{itemize}\\ \hline
Expected result & 
	The user will be shown a list of availible rooms for the selected timeframe. The user can book a room from the list. The calendar will remove the booking from the list if the appointment is cancelled or deleted from the calendar.\\ \hline
Testing task & 
\begin{enumerate}
    \item The user inputs the desired timeframe.
    \item The user books a meeting room from the returned list of availible rooms.
    \item The user cancels the meeting.
    \item The user deletes the meeting.
\end{enumerate}\\ \hline
Necessary environmental requirements & The user must be logged into the system. The user is in the process of making an appointment. \\ \hline
Any dependency between this test and the other tests defined & Tests 1,2, and 5.  \\ \hline

\end{tabularx}

\begin{tabularx}{\textwidth}{ |X|X| }
\hline
\rowcolor{Gray}
Test ID & \#11 \\ \hline
Test item & Visibility \\ \hline
Approach & The calendar client should show a weekly calendar with all appointments in the employees personal calendar. Changing weeks should be easy. \\ \hline
Item pass/ fail criteria & When looking at the calendar all appointments will be shown on a week by week basis. It's possible to navigate between weeks. \\ \hline
Input data & Show selected week\\ \hline
Expected result & The client should show a week view of the calendar. The user should be able to navigate between weeks. \\ \hline
Testing task & 
\begin{enumerate}
    \item The client shows the users appointment this week.
    \item The user can select a different week and see the appointments for that week.\\ \hline
\end{enumerate}
Necessary environmental requirements & The user must be logged into the system. \\ \hline
Any dependency between this test and the other tests defined & Tests 1 and 7. \\ \hline


\end{tabularx}

\begin{tabularx}{\textwidth}{ |X|X| }
\hline
\rowcolor{Gray}
Test ID & \#12 \\ \hline
Test item & Track appointment requests \\ \hline
Approach & The calendar client should indicate in the weekly calendar if your appointment is waiting for reply from one or more participants; if one or more have denied your meeting request; if everyone have accepted your meeting request. \\ \hline
Item pass/ fail criteria & When viewing a week there will be an indication that shows replies from the other participants. (Appointment indicated in colour, i.e.: green if everyone will participate, yellow if missing replies?) \\ \hline
Input data & Show selected week\\ \hline
Expected result & The client should show a week view of the calendar. Replies should be indicated on appointment? \\ \hline
Testing task & 
\begin{enumerate}
    \item The client gives an indication in the week calendar if an appointment is waiting for other participants to reply.
    \item The client gives an indication in the week calendar if an appointment has been denied by one or more participants. \\ \hline
    \item The client gives an indication in the week calendar if an appointment has been accepted by all participants.
\end{enumerate}
Necessary environmental requirements & The user must be logged into the system. There must be one or more appointments created. \\ \hline
Any dependency between this test and the other tests defined & Tests 1, 8, 9 and 11. \\ \hline


\end{tabularx}


\end{document}
