\documentclass[a4paper, 10pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[norsk]{babel}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{float}

\definecolor{Gray}{gray}{0.9}

\begin{document}
\input{title.tex}
\thispagestyle{empty}

\pagenumbering{roman}
\setcounter{page}{0}
\newpage
\tableofcontents

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

\section{Time}

\section{Systemtesting}

\subsection{Results}

\subsection{Changes}

\section{Experiences}

\subsection{Negative experiences}
\subsubsection{Bad communication}
A negative experience from this project has been bad communication between the members in the group, especally with the members that has been sick or unavailable a lot. This has resulted in many a lot of working hours that has just been used for catching up and updating them unnecessary. Between the groupmembers that have been meeting regulary the problem has been mainly that they have not spoken of what they are doing and how far they have come. This has resulted in a little unbalance workload between some parts of the program. Another problem has also been that people has not asked for help instead of hitting the wall with a problem over and over.
\subsubsection{Meeting in time}
A problem for most members in the group is to meet at time, or meeting at all. Very many members are deep sleepers, and sleep right through their alarm. This has resulted in many meetings not starting as late as one hour after the agreed meeting time.

\subsection{Positive experiences}
\subsubsection{New friends}
The members of the group has come very well along right from the start. And we would all say that a very positive experience is that we have been able to make friends across the different studies we are enrolled in. A very good thing about this is that we have been able to work togheter closly every day in a longer time periode without wanting to kill oneanother.

\subsubsection{New knowledge}
From the first meeting we had we discussed the different roles that coding the project would include and who was interested in what. Every member quickly selected a main area they wanted to focus on and everyone got to work with what they wanted. By choosing an assignment that a member would like to work on, the productivity was rather good. At the point of writing this, every member is realy satisfied with all the new knowledge they have gained. The practice experience in the area of databases, graphical interfaces and networking is very good for the future.



\subsection{What could we do better?}
\subsubsection{Scrum meetings}
Our group have not been very good with regular scrum meetings, this is definitely something we could do better. We see that the negative expericences from bad communication would probably have been eliminated if regular scrummeetings was something we did every day. We ended up with trying to catch up with everything when we had meeting, which resulted in long inefficient meetings. 
\subsubsection{Group leader}
Every group did get a group leader which was assigned by the teaching staff. The group in general did not use this person as the leader, instead we all took responsibility, which in the start worked very well. But at the end of the project it was hard for everyone to keep up with all the loose ends and what need to be done in what order.  Since we had noone that had the overview over the big picture it was realy hard to assaign the different issues that still was around to the people that did not have anything to do. When we look at this problem in retrospective it is easy to see that the group leader role should be assigned and given spesific task to do as we went through the project.

\end{document}
